Simulations

### 2017-11-20 3-simus.Rmd
save

```{r}
if (!dir.exists("results1")) dir.create("results1")

@@

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple"),
    ttrees(TTree, "backingfiles/ttrees", pheno.all, ind.train, ind.test, n.trees = 100)
  )
  print(res)
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

### Second simulations (without T-Trees)

```{r}
params.grid2 <- expand.grid(
  par.causal = list(c(30, "all"), c(300, "all"), c(3000, "all"), c(30, "HLA")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = c(0.5, 0.8), 
  par.model  = c("simple", "fancy"),
  num.simu   = 1:50,
  stringsAsFactors = FALSE
) 
```

```{r, eval=TRUE}
if (!dir.exists("results2")) dir.create("results2")

@@

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple")
  )
  print(res)
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

@@

@@

@@

  # Get results from all methods
  res <- bind_rows(
    PRS(G6, CHR[CHR == 6], POS[CHR == 6], pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G6, pheno.all, covar.all, ind.train, ind.test, "logit-simple")
  )
  print(res)
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

>>>>

```{r, eval=FALSE}
if (!dir.exists("results1")) dir.create("results1")

@@

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple"),
    ttrees(TTree, "backingfiles/ttrees", pheno.all, ind.train, ind.test, n.trees = 100)
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

### Second simulations (without T-Trees, with logit-triple)

```{r}
params.grid2 <- expand.grid(
  par.causal = list(c(30, "all"), c(300, "all"), c(3000, "all"), c(30, "HLA")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = c(0.5, 0.8), 
  par.model  = c("simple", "fancy"),
  num.simu   = 1:20,
  stringsAsFactors = FALSE
) 
```

```{r, eval=FALSE}
if (!dir.exists("results2")) dir.create("results2")

@@

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple")
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

### Third simulations (without logit-triple)

```{r}
params.grid3 <- expand.grid(
  par.causal = list(c(30, "all"), c(300, "all"), c(3000, "all"), c(30, "HLA")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = c(0.5, 0.8), 
  par.model  = c("simple"),
  num.simu   = 21:100,
  stringsAsFactors = FALSE
) 
```

@@

for (i in rows_along(params.grid3)) {

  params <- params.grid3[i, ]
  par.causal <- params[["par.causal"]][[1]]

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple")
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

### Fourth simulations (dataset with only chromosome 6)

```{r}
params.grid4 <- expand.grid(
  par.causal = list(c(30, "all"), c(300, "all"), c(3000, "all"), c(30, "HLA")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = c(0.5, 0.8), 
  par.model  = c("simple"),
  num.simu   = 1:100,
  stringsAsFactors = FALSE
) 
```

```{r, eval=FALSE}
if (!dir.exists("results4")) dir.create("results4")

@@

for (i in rows_along(params.grid4)) {

  res.file <- paste0("results4/simu_", i, ".rds")
  if (file.exists(res.file)) next

  params <- params.grid4[i, ]
  par.causal <- params[["par.causal"]][[1]]

@@

  # Get results from all methods
  res <- bind_rows(
    PRS(G6, CHR[CHR == 6], POS[CHR == 6], pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G6, pheno.all, covar.all, ind.train, ind.test, "logit-simple")
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

### Fifth simulations (varying training size)

```{r}
params.grid5 <- expand.grid(
  n.train    = 1:5 * 1000,
  par.causal = list(c(300, "all")), 
  par.dist   = c("gaussian", "laplace"), 
  par.h2     = c(0.5, 0.8), 
  par.model  = c("simple"),
  num.simu   = 1:100,
  stringsAsFactors = FALSE
) 
```

```{r, eval=TRUE}
if (!dir.exists("results5")) dir.create("results5")

for (i in rows_along(params.grid5)) {

  res.file <- paste0("results5/simu_", i, ".rds")
  if (file.exists(res.file)) next

  params <- params.grid5[i, ]
  par.causal <- params[["par.causal"]][[1]]

  # Split in training/test sets
  ind.train <- sort(sample(n, size = params[["n.train"]]))
  ind.test <- setdiff(1:n, ind.train)

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple")
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```
